The role of cognateness in non-native spoken word recognition

### 2022-03-16 manuscript/manuscript.Rmd
Minor refactoring
WIP

We measured the phonological similarity between translation pairs by computing the Levenshtein similarity between their IPA translations using the `stringsim` function of the stringdist R package [@van2014stringdist]. This function computes the inverse of the Levenshtein distance between two character strings as a proportion. First, it computes the edit distance between two character strings (in this case, phoneme symbols) by counting the number of additions, deletions, and substitutions necessary to make both strings identical [@levenshtein1966binary]. This measure is then divided by the maximum distance (according to the length of the longest string) and then subtracted from 1. The result is percentage score indicating no similarity between the two strings if 0%, and a perfect match between two strings if 100%. We computed this similarity measure (Levenshtein, from now on) for every translation pair in our stimuli lists. For example, the *table* (teɪbəl)-*mesa* (mesa) translation pair had a `r percent(stringsim("teɪbəl", "mesa"))` similarity, while the *train* (trEIn)-*guitarra* (tɾEn) translation pair had a `r percent(stringsim("trEIn", "tɾEn"))` similarity. Figure 1 summarises the lexical frequency, phonological neighbourhood density and phonological overlap of the words included in the Catalan and the Spanish lists.

@@

$$
\begin{align}

@@

\end{align}
$$

>>>>

We measured the phonological similarity between translation pairs by computing the Levenshtein similarity between their IPA translations using the `stringsim` function of the stringdist R package [@van2014stringdist]. This function computes the inverse of the Levenshtein distance between two character strings as a proportion. First, it computes the edit distance between two character strings (in this case, phoneme symbols) by counting the number of additions, deletions, and substitutions necessary to make both strings identical [@levenshtein1966binary]. This measure is then divided by the maximum distance (according to the length of the longest string) and then subtracted from 1. The result is percentage score indicating no similarity between the two strings if 0%, and a perfect match between two strings if 100%. We computed this similarity measure (Levenshtein, from now on) for every translation pair in our stimuli lists. For example, the *table* (teɪbəl)-*mesa* (mesa) translation pair had a `r percent(stringsim("teɪbəl", "mesa"))` similarity, while the *train* (trEIn)-*tren* (tɾEn) translation pair had a `r percent(stringsim("trEIn", "tɾEn"))` similarity. Figure 1 summarises the lexical frequency, phonological neighbourhood density and phonological overlap of the words included in the Catalan and the Spanish lists.

@@

$$\begin{align}

@@

\end{align}$$
